Open Data, Open Source and Open Standards in chemistry - The Blue Obelisk five years on

### 2011-04-22 paper.tex
Improved section on web based tools and ChemDoodle Web Components. Added ChemDoodle Web Components to projects table. I don't know where to place references, but the urls are as follows:
ChemDoodle Web Components - http://web.chemdoodle.com
HTML5 - http://dev.w3.org/html5/spec/

One important aspect of the above
toolkits is that they originated for the support of desktop
and server-side applications. More recently, a number of workers have developed light-weight
toolkits that are targeted towards web applications. One example of
this form is the ChemDoodle library from iChemLabs. The focus of these
toolkits is to support client-side cheminformatics functionality,
allowing for rich, chemically-aware browser-based applications.

@@

%% Use of \listoftables is discouraged.
%%
\section*{Tables}
  \subsection*{Table 1 - Blue Obelisk Open Source software projects}
    (Description if necessary XXXXXXXXXXXXXXX. Add citations to project names.)
    \par \mbox{}
    \par
    \mbox{
      \begin{tabular}{|c|c|c|}
        %% \hline \multicolumn{3}{|c|}{My Table}\\ \hline
        \hline Name & Website & Description? or Lead Developer? \\ \hline
        \multicolumn{3}{|c|}{Cheminformatics toolkits} \\ \hline
        Chemistry Development Kit (CDK) \cite{Steinbeck2003, Steinbeck2006} & http://cdk.sf.net & XXXX  \\ \hline
        Cinfony & http://cinfony.googlecode.com & Noel O'Boyle, Python interface to toolkits \\ \hline
        Indigo & http://ggasoftware.com/opensource/indigo & GGA Software \\ \hline
        Open Babel & http://openbabel.org & Geoffrey Hutchison et al \\ \hline
        RDKit & http://rdkit.org & Greg Landrum \\ \hline
        \multicolumn{3}{|c|}{Integration} \\ \hline
        CDK-Taverna \cite{Kuhn:2010p4001} & http://cdk-taverna.blah.XXX & Christoph Steinbeck, Workflow \\ \hline
        A3 & ..  & .  \\ \hline
        \multicolumn{3}{|c|}{Interconversion} \\ \hline
        OSRA & http://osra.sf.net & Igor Filippov, Image to structure \\ \hline
        OPSIN & http://opsin.ch.cam.ac.uk & Daniel Lowe, Name to structure \\ \hline
        A3 & ..  & .  \\ \hline
        \multicolumn{3}{|c|}{Structure Databases} \\ \hline
        OrChem \cite{RijnbeekS10} & http://orchem.sourceforge.net & Christoph Steinbeck, Oracle-based Chemical Database Engine \\ \hline
        MyChem  & http://XXX.sourceforge.net & Jerome Pansanel, MySQL-based Chemical Database Engine \\ \hline
        PGChem  & http://XXX.sourceforge.net & Ernst-Georg Schmid, PostgreSQL-based Chemical Database Engine \\ \hline
        Bingo  & http://XXX.XXX.XXX & Dmitry Pavlov, Oracle-based Chemical Database Engine \\ \hline

>>>>

While desktop software has composed the majority of scientific tools since the computer was introduced, the internet continues to change how applications and content are distributed and presented. As such, there is a growing need to present chemical and scientific information in a web-based medium. Recently, a new version of the HTML specification, HTML5 \cite{html5}, defines a well-developed framework for creating native web applications in Javascript. This native framework provides a significant benefit to scientists as the web is an open and free medium to distribute scientific knowledge, ideas and education. It also poses significant new problems, as the cost associated with learning and developing tools for new technologies is not trivial. As such, it is an important goal for the Blue Obelisk to provide such tools and encourage the community to utilize these new technologies to improve products and education. A specific example of this initiative is the ChemDoodle Web Components library \cite{ChemDoodleWeb}, produced by iChemLabs. The ChemDoodle Web Components library is open source under the GPL v3 license with a liberal HTML exception. ChemDoodle Web Components allow the scientist to present publication quality 2D and 3D graphics and animations for chemical structures, reactions and spectra. Beyond graphics, this tool provides a framework for user interaction to create dynamic applications through web browsers, desktop platforms and mobile devices such as the iPhone, iPad and Android devices. It is now easier than ever for scientists to create web-based scientific content, without having to master complicated technologies such as Java applets. iChemLabs is dedicated to funding, developing and supporting the library to ensure that the next generation of scientific applications is easily achievable by academia, government and industry. This goal helps to make sure that the cost of education decreases while using the web to further spread science.

@@

%% Use of \listoftables is discouraged.
%%
\section*{Tables}
  \subsection*{Table 1 - Blue Obelisk Open Source software projects}
    (Description if necessary XXXXXXXXXXXXXXX. Add citations to project names.)
    \par \mbox{}
    \par
    \mbox{
      \begin{tabular}{|c|c|c|}
        %% \hline \multicolumn{3}{|c|}{My Table}\\ \hline
        \hline Name & Website & Description? or Lead Developer? \\ \hline
        \multicolumn{3}{|c|}{Cheminformatics toolkits} \\ \hline
        Chemistry Development Kit (CDK) \cite{Steinbeck2003, Steinbeck2006} & http://cdk.sf.net & XXXX  \\ \hline
        Cinfony & http://cinfony.googlecode.com & Noel O'Boyle, Python interface to toolkits \\ \hline
        Indigo & http://ggasoftware.com/opensource/indigo & GGA Software \\ \hline
        Open Babel & http://openbabel.org & Geoffrey Hutchison et al \\ \hline
        RDKit & http://rdkit.org & Greg Landrum \\ \hline
        ChemDoodle Web Components & http://web.chemdoodle.com & iChemLabs \\ \hline
        \multicolumn{3}{|c|}{Integration} \\ \hline
        CDK-Taverna \cite{Kuhn:2010p4001} & http://cdk-taverna.blah.XXX & Christoph Steinbeck, Workflow \\ \hline
        A3 & ..  & .  \\ \hline
        \multicolumn{3}{|c|}{Interconversion} \\ \hline
        OSRA & http://osra.sf.net & Igor Filippov, Image to structure \\ \hline
        OPSIN & http://opsin.ch.cam.ac.uk & Daniel Lowe, Name to structure \\ \hline
        A3 & ..  & .  \\ \hline
        \multicolumn{3}{|c|}{Structure Databases} \\ \hline
        OrChem \cite{RijnbeekS10} & http://orchem.sourceforge.net & Christoph Steinbeck, Oracle-based Chemical Database Engine \\ \hline
        MyChem  & http://XXX.sourceforge.net & Jerome Pansanel, MySQL-based Chemical Database Engine \\ \hline
        PGChem  & http://XXX.sourceforge.net & Ernst-Georg Schmid, PostgreSQL-based Chemical Database Engine \\ \hline
        Bingo  & http://XXX.XXX.XXX & Dmitry Pavlov, Oracle-based Chemical Database Engine \\ \hline
